---
title: "Project 1 Notebook"
output: html_notebook
---

# Load in packages
```{r}
library(tidyverse)
library(sqldf)
library(lubridate)
```

# Load in Data

Using SQL due to size of data and only small amount we need
```{r}
power <- read.csv.sql("household_power_consumption.txt",
                  sql = "select * from file where Date = '1/2/2007' or Date = '2/2/2007'",
                  sep = ";")


power <- mutate(power,
                datetime = strptime(
                  paste(Date, Time),"%d/%m/%Y %H:%M:%S"))
colnames(power)
```

# Plot1.png

Histogram, 12 bins
title = "Global Active Power
xlabel = Global Active Power (kilowatts)
ylabel = "Frequency

```{r}
png(filename = "plot1.png",
    width = 480, height = 480)
hist(power$Global_active_power, col = "red",
     main = "Global Active Power",
     xlab = "Global Active Power (kilowatts)")
dev.off() # close png device for next plot
```

# Plot2.png

lineplot?

xticks = Thu, Fri, Sat
ylabel = "Global Active Power (kilowatts)"

```{r}
png(filename = "plot2.png", width = 480, height = 480)

plot(power$datetime, power$Global_active_power,
                 xlab = "",
                 ylab = "Global Active Power(kilowatts)",
                 type = "l")

dev.off() # close png device for next plot

```

# Plot3.png

Combination of 3 line plots

- Sub_metering_1 in black
- Sub_metering_2 in red
- Sub_metering_3 in blue

ylabel = "Energy sub metering"
xticks = "Thu", "Fri", "Sat"

legend in top right

```{r}
png(filename = "plot3.png", width = 480, height = 480)

par(mfrow = c(1, 1))


plot(power$datetime, power$Sub_metering_1, col = "black",
     type = "l", xlab = "", ylab = "Energy sub metering")

lines(power$datetime, power$Sub_metering_2, col = "red",
     xaxt = "n", yaxt = "n")

lines(power$datetime, power$Sub_metering_3, col = "blue",
     xaxt = "n", yaxt = "n")

legend("topright",
       legend = c("Sub_metering_1",
                  "Sub_metering_2",
                  "Sub_metering_3"),
       col = c("black", "red", "blue"),
       lty = 1)

dev.off() # close png device for next plot
```

# Plot4.png
A 2,2 multiplot

1: plot2
2: lineplot Voltage against datetime
3: plot3
4: lineplot global_reactive_power against datetime

```{r}
png(filename = "plot4.png", width = 480, height = 480)

par(mfrow = c(2, 2))

# Plot 1
plot(power$datetime, power$Global_active_power,
                 xlab = "",
                 ylab = "Global Active Power(kilowatts)",
                 type = "l")


# Plot 2
plot(power$datetime, power$Voltage,
     xlab = "datetime", ylab = "Voltage", type = "l")


# Plot 3
plot(power$datetime, power$Sub_metering_1, col = "black",
     type = "l", xlab = "", ylab = "Energy sub metering")

lines(power$datetime, power$Sub_metering_2, col = "red",
     xaxt = "n", yaxt = "n")

lines(power$datetime, power$Sub_metering_3, col = "blue",
     xaxt = "n", yaxt = "n")

legend("topright",
       legend = c("Sub_metering_1",
                  "Sub_metering_2",
                  "Sub_metering_3"),
       col = c("black", "red", "blue"),
       lty = 1)

# Plot 4
plot(power$datetime, power$Global_reactive_power,
     xlab = "datetime", ylab = "Global_reactive_power",
     type = "l")

dev.off() # close png device for next plot

```